Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-20 paper.tex

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
`molecular workbench' for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for invoking functionality or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as for example Brunn~\cite{Brunn}, which is a laboratory information
system for microplate based high-throughput screening. In this manner open
source projects empower other open source projects.

>>>>

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
molecular workbench for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for scripted research or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as Brunn~\cite{Brunn}, which is a laboratory information system for
microplate based high-throughput screening. In this manner open source projects
empower other open source projects.
